\documentclass[char]{FDD}
\parindent=0pt
\begin{document}
\name{\cTohsaka{}}

\textbf{You}
You are the oldest of the children in your generation. Your selection as the master was a surprise however, as your father was the youngest of his generation, and not particularly talented. Your mother and father had moved into a townhouse away from the Tohsaka estate long before you were born.

\textbf{Your Family}
The Tohsaka family is one of the 3 families (along with the Matou and Eizenberg) that originally \textbf{created} the holy grail. The artifact was a massive magical collaboration that was intended to grant access to the Root of the World. The Root of the World is a place out of time and space, the begining of everything. Being able to go there, to study it, would elevate the mage (and their line) who managed it beyond any other family in the world. That kind of prestige is rightfully due the Tohsaka family. And when you are the one to finally do it, after so many generations of trying, you will be the greatest of the greatest families.

The Tohsaka family maintains professional, if not friendly relations with the Mage's Association in London. They have the potential to be powerful allies, but have a distressing tendency to demand the lion's share of any jointly earned spoils. They also have the potential to be terribly dangerous enemies, so your family has always been careful to avoid offering anything that could be perceived as a slight beyond steadfastly refusing to join the Association, pleading distance between London, England and Fuyuki, Japan. It is because of this uneasy balance that you find yourself in an awkward positino with \cRi{\full}, a representative from the Mage's Association. \cRi{} has been sent by the association to ``retrieve" something from each of the estates of the 3 founding families (Tohsaka, Matou, and Eizenberg). You are obliged to help \cRi{\then} "retrieve" these items from the other two families to avoid upsetting the Mage's association, but preventing \cRi{\them} from taking whatever it is from the Tohsaka estate to avoid upsetting your family.

\textbf{Your Servant}
Berserker class Servants are very hard to control. They are incredibly powerful, but tend to be slow and stupid. Even though the magical power that allows Berserker to exist for this war comes from you, it must never be far from your mind that a Berserker class Servant is the most likely to turn on their Master and kill them. 

Your servant is \cBerserker{}, of the biblical story of \cAssassin{} and \cBerserker{}. \cBerserker{\They} \cBerserker{\are} determined to win the Holy Grail War and wish for the 

\begin{itemz}[Goals]
	\item Win the Holy Grail War (be the last pair or individual alive/still competing), and wish for access to the Root of the World.
	\item Get the Mage's Association off of your back by helping \cRi{\full} retrieve whatever it is i{\they} want from the Matou and Eizenberg estates.
	\item Prevent \cRi{} from retrieving whatever it that they want from the Tohsaka estate.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cBerserker{}}
	\contact{\cMatou{}}
	\contact{\cEizenberg{}}
	\contact{\cRi{}}
	\contact{\cArchibald{}} The Church Arbiter, who is monitoring the war. \cArchibald{\They} have left no strong impression on you. 
\end{contacts}

\end{document}
